Visualizations for the manuscript

### 2022-05-17 metanalysis_visualization/manuscript_Figures.Rmd
modify the sex ITS plot to show only females. fix the eating disorder plot, not showing the dots after renaming the category

#### Alternative plot 
```{r, include=FALSE}
plot_annotations_sex_df2 <- data.frame(term=c("difference_solpe","difference_solpe"),
                                       sex=c("female", "male"),
                                       label=c("Coefficient difference: 0.77 (pvalue: <0.01)", "Coefficient difference: -0.77 (pvalue: 0.005)"),
                                       plotsLabel=c("Female", "Male"))

bootstrapped_fitted_sex %>% 
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             #scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df2, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 25, units = "cm")
```

@@

perc_disorder_group_total$disorder_group <- gsub( "Feeding and Eating Disorders", "Eating Disorders", perc_disorder_group_total$disorder_group)
```

>>>>

#### Alternative plot 
```{r, include=FALSE}
#plot_annotations_sex_df2 <- data.frame(term=c("difference_solpe","difference_solpe"),
#                                       sex=c("female", "male"),
#                                       label=c("Coefficient difference: 0.77 (pvalue: <0.01)", "Coefficient difference: -0.77 (pvalue: 0.005)"),
#                                       plotsLabel=c("Female", "Male"))

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 25, units = "cm")
```

@@

perc_disorder_group_total$disorder_group <- gsub( "Feeding and Eating Disorders", "Eating Disorders", perc_disorder_group_total$disorder_group)

disorders_to_select <- c(
  "Anxiety Disorders", 
  "Depressive Disorders", 
  "Eating Disorders", 
  "Suicide or Self-Injury"
)
```
